Taxonomic bias can create spurious results in microbiome differential-abundance analyses unless it is properly accounted for

### 2021-06-24 models.Rmd
Put non-article chapters in the appendix
Fix typo

@@

To consider various addition information that can be used for absolute abundance inference, I let $B$ denote bulk abundance measurements (such as via flow cytometry or broad-range 16S qPCR), $S$ genome the known taxon abundances of a spike-in, and $T$ denote the abundances of a set of taxa made via targeted measurement.
I let $R \subset \{1, \dots, I\}$ denote the set of _reference taxa_ whose abundance is known independently from the metagenomics measurement (up to experimental bias factors) because they were spiked at a known density, subjected to a targeted measurement, or have been determined through some other means to have a constant or known abundance across samples.

>>>>

# (APPENDIX) Appendix {-}

@@

To consider various addition information that can be used for absolute abundance inference, I let $B$ denote bulk abundance measurements (such as via flow cytometry or broad-range 16S qPCR), $S$ denote the known taxon abundances of a spike-in, and $T$ denote the abundances of a set of taxa made via targeted measurement.
I let $R \subset \{1, \dots, I\}$ denote the set of _reference taxa_ whose abundance is known independently from the metagenomics measurement (up to experimental bias factors) because they were spiked at a known density, subjected to a targeted measurement, or have been determined through some other means to have a constant or known abundance across samples.
